\subsection{TOF Data Reduction}
\label{sec:TOFDataReduction}
Even if the average payload per event of the TOF raw data format is quite limited it is not
completely optimized. This is due in particular to some intrinsic limitations of the existing hardware
of the TDC readout modules (TRM) which have on board legacy FPGAs (Actel ProAsicPlus\circledR APA750). 
With a much larger amount of data read-out a further optimization is obviously desirable.
However these cards will not be replaced as part of the upgrade program and an optimization with the current FPGAs
resulted impossibile.

The data format is currently made by a structure of control words (6 words for each TRM) encapsulating the hit
information (two words for each hit registered by the detector), providing addressing for hit encapsulated - if any - 
and validating the readout, including CRC controls on data potentially exposed to Single Event Upsets in internal staging FIFOs). 
This approach proved robust but due to the presence of these control words even an entirely ``empty'' event 
(no hit registered at TOF) has - however - a 21 KB raw data size. The control words contain also certain slow control information 
(such as temperatures of the cards and thresholds set on front-end cards) which can be stripped: the slow control part is already 
actually read-out via a devoted optical link and saved separately.

Several data reduction options are therefore possible inserting immediate processing at FLP level, with a greater
impact foreseen in \pp collisions, where the event multiplicity is smaller.
Different algorithms will be tested and their performance evaluated during RUN2 implementing them
inside the HLT. With respect to the standard numbers (e.g. maintaining the current format) 
we expect to achieve a 50\% data reduction in \pp and less in \pbpb (with data reduction performance
decreasing for the most central events where the pure 'hit payload' is however dominant). In Table~\ref{tab:InputRate} we tentatively
indicated a 20\% gain in \pbpb and we assumed an average 2000 hits multipicity at TOF in minimum bias. It must be taken into
account, finally, that the whole payload for TOF is also subject to some uncertainty in \pbpb depending on the actual bunch spacing scheme
that will be adopted by the LHC for heavy ions collisions.
